%!TEX TS-program = xelatex

% use only XeLaTeX or LuaLaTeX to compile
\documentclass[a4paper]{comcv}

\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{xparse}
\usepackage{amsfonts}


\tolerance=10000
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\exhyphenpenalty=10000

\ExplSyntaxOn

\NewDocumentCommand{\getenv}{om}
 {
  \sys_get_shell:nnN { kpsewhich ~ --var-value ~ #2 } { } \l_tmpa_tl
  \tl_trim_spaces:N \l_tmpa_tl
  \IfNoValueTF { #1 }
   {
    \tl_use:N \l_tmpa_tl
   }
   {
    \tl_set_eq:NN #1 \l_tmpa_tl
   }
 }

\ExplSyntaxOff
\getenv[\EMAIL]{EMAIL}

\title{Dan Zimmerman's CV}
\fullname{Dan}{Zimmerman}{}
\cvtitle{}
\website{https://danz.im}{danz.im}
\email{\EMAIL}
\github{https://github.com/danzimm}{danzimm}
\linkedin{https://www.linkedin.com/in/danzimm}{danzimm}
\currentdate{\today}

\begin{document}

\section{Education}

\combosection{M.S. in Mathematics}{Loyola University Chicago}{Spring 2025}{
  \noindent\hangindent=1.5em\hangafter=1
  {\regular Coursework}: {\italic Differential Geometry (Guillemin \& Pollack); Functional Analysis (Bachman); Topology (Munkres); \\ Real Analysis II (Rosenlicht); Optimization (Guenin); Game Theory (Barron); Automata \& Formal Languages (Sipser)}

  {\regular GPA}: 3.89/4.0

  \vspace{\topsep}
}

\combosection{B.S. in Theoretical Physics, Mathematics}{Loyola University Chicago}{Spring 2015}{
  \noindent\hangindent=1.5em\hangafter=1
  {\regular Selected coursework}: {\italic Quantum Mechanics (Griffiths); E\&M (Griffiths); Mechanics (Thornton \& Marion); PDEs (Brezis); \\ Complex Analysis (Saff \& Snider); Real Analysis I (Rudin) }

  {\regular Major GPA}: 3.76/4.0
}


\vspace{\topsep}

\section{Research}

\combosection{Asymptotic Limits of Nonlocal Curvature for Curves}{LUC (B. Seguin)}{2023 - Present}{
  \begin{tightlist}
    \item
      Recovered classical curvature under appropriate limit of nonlocal curvature for circles in $\mathbb{R}^n$.
    \item
      Investigating recovering classical curvature under similar limit for arbitrary, sufficiently regular curves in $\mathbb{R}^n$.
    \item
      {\italic \href{https://github.com/danzimm/math/blob/main/analysis/curvature.pdf}{Work in progress manuscript}.}
  \end{tightlist}
}

\combosection{Supernova Photometric Contamination Studies}{ANL (S. Kuhlmann, J. Cunningham)}{2013 - 2015}{
\begin{tightlist}
\item
  Reduced false-positive Type Ia identifications by approximately 50\% by leveraging novel statistical software (SNCosmo) which allowed us to more granularly classify lightcurves.
\item
  Investigated contamination of photometrically-selected Type Ia supernova samples by core-collapse supernovae using SNANA simulations and SALT2 parameter-space selection. Identified misclassified SNcc events and applied SNCosmo template-fitting with various characteristic lightcurves (\href{https://github.com/danzimm/sim_typing/}{code}).
\end{tightlist}
}

\section{Presentations}

\combosection{Computing the limit of the Nonlocal Curvature}{\href{https://www.ams.org/meetings/sectional/2317_program_ss16.html}{AMS Fall Eastern Sectional Meeting}}{2024}{
  \noindent\hangindent=1.5em\hangafter=1
  {\href{https://github.com/danzimm/math/blob/main/ams_fall_2024/ams_fall_2024.pdf}{Oral presentation} exploring computing the limit of nonlocal curvature of curves in $\mathbb{R}^n$, discussing current results and the conjecture we're actively working on relating classical and nonlocal notions of curvature.}

}
\vspace{\topsep}

\combosection{IODI: Instruction offset Debug Information}{Facebook}{2019}{
  \noindent\hangindent=1.5em\hangafter=1
  {Oral presentation on a \href{https://github.com/facebook/redex/blob/5dfb66d950d672908a3961d43a9e3473cac48353/libredex/IODIMetadata.h}{compiler optimization that compresses data}. Presentation demonstrated the source of low entropy, described how to increase entropy, contained reduction measurements and discussed the project plan from conception to implementation.}

}

\vspace{\topsep}

\combosection{Quantum Turing Machines and Shor's Algorithm}{Loyola University of Chicago}{2016}{
  \noindent\hangindent=1.5em\hangafter=1
  {\href{https://github.com/danzimm/cv/blob/main/QTM.key}{Final oral presentation} for Automata and Formal Languages course. The slides were paired with derivations on the board.}

}

\vspace{\topsep}

\combosection{\phantom{Photometric Classification of Supernovae}}{\href{https://aas.org/sites/default/files/2020-01/AAS_225_Meeting_Program.pdf}{American Astronomical Society 225th Meeting}}{2015}{}
\vspace{-1.2 \topsep}

\combosection{Photometric Classification of Supernovae}{\href{https://www.caurs.com}{Chicago Area Undergraduate Research Symposium}}{2015}{}
\vspace{-1.2 \topsep}

\combosection{\phantom{Photometric Classification of Supernovae}}{\href{https://www.cur.org/events-services/ncur/}{National Conference on Undergraduate Research}}{2014}{
  \noindent\hangindent=1.5em\hangafter=1
  {\href{https://github.com/danzimm/cv/blob/main/aas225.pdf}{Poster presentation} showing approximately 50\% total reduction of incorrect identification of Type Ia Supernovae light curves via using novel statistical software (SNCosmo) and introducing better cuts.}

}

\vspace{\topsep}

\combosection{Dirichlet's principle}{\href{https://www.ias.edu/pcmi}{IAS Undergraduate Summer School at PCMI}}{2014}{
  \noindent\hangindent=1.5em\hangafter=1
  \href{https://github.com/danzimm/cv/blob/main/dirichlet.pdf}{Oral presentation} where it was shown that minimizing the Dirichlet energy $\int \lVert \nabla u \rVert^2 - fu$ and solving Poisson's equation ${-\Delta u = f}$ is equivalent.

}

\vspace{\topsep}

\section{Awards \& Distinctions}

\combosection{Father Gerst Memorial Award Excellence in Physics}{LUC}{2015}{
  \noindent\hangindent=1.5em\hangafter=1
  {\href{https://www.luc.edu/physics/undergraduateexperiences/departmentawards/}{Award} established in 1965 in honor of Fr. Francis J. Gerst, S.J., former Chair of Mathematics and Dean of the Graduate School; presented to students in the physics program for {\regular outstanding academic excellence in physics}.}

}

\vspace{\topsep}

\combosection{Interdisciplinary Honors Program}{LUC}{2012 - 2015}{
  \noindent\hangindent=1.5em\hangafter=1
  {Completed Loyola’s \href{https://www.luc.edu/honors/aboutus/}{Interdisciplinary Honors Program}, a {\regular selective, competitive, intensive curriculum emphasizing \\ analytical and communication skills}, international and interdisciplinary perspectives, and high academic performance \\ (including additional honors coursework and GPA requirements).}

}

\vspace{\topsep}

\combosection{IAS Undergraduate Summer School}{PCMI}{2014}{
  \noindent\hangindent=1.5em\hangafter=1
  {{\regular Competitively selected participant} in the \href{https://www.ias.edu/pcmi}{IAS/PCMI Undergraduate Summer School}, an intensive program featuring \\ advanced mathematical lectures by leading researchers. The program culminated in the presentation mentioned above.}

}

\vspace{\topsep}

\section{Applied Research in Industry}

\combosection{Android Binary Size Investigations}{Facebook}{2019}{
  \noindent\hangindent=1.5em\hangafter=1
  {Identified low-entropy debug-information regions in Android binaries and demonstrated that compiler transformations could raise entropy and reduce size (\href{https://github.com/facebook/redex/blob/5dfb66d950d672908a3961d43a9e3473cac48353/libredex/IODIMetadata.h}{IODI}, see presentation above).}

}

\combosection{Javascript Startup Execution Analysis}{Facebook}{2018}{
  \noindent\hangindent=1.5em\hangafter=1
  {Characterized memory-constrained execution paths unique to mobile environments, localized inefficient regions and proposed entropy-increasing optimizations to reduce startup latency. Implemented optimizations (string interning) in \href{https://github.com/facebook/hermes}{Hermes Javascript Virtual Machine}}

}

\vspace{\topsep}

\combosection{iOS Startup Execution Analysis}{Facebook}{2018}{
  \noindent\hangindent=1.5em\hangafter=1
  {Used performance profilers to trace memory-faulting patterns introduced by proprietary compiler optimizations. Research culminated in internal technical report detailing measurements of performance issues, proving the source of the slowdown was decreased entropy and included steps to reproduce the results.}

}

\vspace{\topsep}

\section{Industry}

\vspace{2mm}

\begin{center}
  My work focuses on applying programming-language \& information-theoretic analysis to optimization problems.
\end{center}

\combosectionz{Meta}{Software Engineer}{AI Software Platform}{Jan 2024 - Present}{
  %Worked on AI infrastructure with a focus on reliability, correctness and performance.
  %\vspace{\topsep}
  \begin{tightlist}
    \item Scaled MI300 GPUs across Meta’s fleet by updating algorithms to match Nvidia-class performance and accuracy.
    \item Improved \href{https://github.com/triton-lang/triton}{Triton} kernel performance on MI300 hardware by exploiting architecture-specific features.
    \item Expanded and stabilized Triton’s frontend to simplify GPU kernel authoring.
  \end{tightlist}
}

%\vspace{\topsep}

\combosectionz{Adyen}{Staff Software Engineer}{Mobile + POS Terminals}{May 2023 - Dec 2023}{
  \begin{tightlist}
    \item Founding engineer in Adyen’s first U.S. office; strengthened the site’s engineering influence.
    \item Drove org-wide best practices, unified Mobile \& POS Terminals via shared APIs, and established strong product–engineering communication workflows.
  \end{tightlist}
}

%\vspace{\topsep}

\combosectionz{Spotify}{Senior Software Engineer}{iOS Performance}{Apr 2022 - Jan 2023}{
  \begin{tightlist}
    \item Enhanced iOS startup instrumentation and system-level diagnostics, improving observability and app reliability.
    \item Developed Early Quality Tests to identify subtle and hard-to-detect performance regressions.
  \end{tightlist}
}

\combosectionz{Snap}{Senior Software Engineer}{iOS Performance, CI Infrastructure}{May 2020 - Feb 2022}{
  \begin{tightlist}
    \item Built local and production performance instrumentation adopted by dozens of teams.
    \item Improved app startup time by 5–10\% through targeted I/O optimizations.
    \item Designed and implemented Python-based CI infrastructure to improve testing, reliability and debuggability.
  \end{tightlist}
}

\combosectionz{Facebook}{Senior Software Engineer}{iOS + Android Performance}{May 2017 - May 2020}{
  \begin{tightlist}

    \item
      Delivered 5–40\% CPU, I/O, and startup performance improvements across large-scale mobile systems through profiling-guided optimizations, bytecode analysis, and \href{https://android-review.googlesource.com/q/owner:danzimm\%2540fb.com}{AOSP} on-device PGO.
    \item
      Designed and implemented Objective-C and Android bytecode compiler optimizations, including Obj-C++ codegen fixes (\href{https://reviews.llvm.org/D41050}{D41050}, \href{https://reviews.llvm.org/D59873}{D59873}) and debug-info reductions that cut binaries by 4–20\%.
    \item
      Built large-scale performance modeling frameworks (clustering + regression) to analyze system behavior and guide engineering decisions.
  \end{tightlist}
}

\combosectionz{Arity}{Application Developer}{iOS}{Jul 2016 - May 2017}{
  \begin{tightlist}
    \item Used PLT techniques to enable experimentation of algorithms in driving-behavior app used by tens of thousands of users.
  \end{tightlist}
}

\combosectionz{StageBloc / Fullscreen}{Mobile Developer}{iOS}{Jul 2016 - May 2017}{
  \begin{tightlist}
    \item Built and maintained production iOS social, shopping, and SVOD applications serving thousands of users.
  \end{tightlist}
}

\combosectionz{Google}{Software Engineer}{iOS}{Aug 2015 – Jan 2016}{
  \begin{tightlist}
    \item Implemented flight and sports cards for the iOS Google Now feature team, used by hundreds of thousands of users.
  \end{tightlist}
}

\section{Beyond}

\combosection{Skills}{}{}{
  \noindent\hangindent=1.5em\hangafter=1
  Python (NumPy, SciPy, Matplotlib, PyTorch, Triton); C/C++; CUDA / GPU Programming; HPC profiling \& performance modeling; Mathematica; \LaTeX; differential-geometric \& variational techniques; asymptotic and measure-theoretic methods.

}

  \vspace{\topsep}

\combosection{Interests}{}{}{
  \noindent\hangindent=1.5em\hangafter=1
  CAD modeling; 3D printing; mechanical mechanisms; neuroscience, philosophy, math, physics literature; kickboxing; rock climbing; coffee; contemporary art; book club.

}

\end{document}
